Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-15 appendix.qmd
Added new projections. Need to update the circle isse

## First projection
projection <- cbind(
    c(-0.4545,-0.5533,-0.1235,0.3984,-0.2065,-0.3586,-0.0088,0.3572,-0.1368),
    c(0.4576,-0.3157,0.4708,0.1410,-0.4479,-0.1685,0.3668,-0.2692,0.1332))

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1.23, 
               highd_data = scaled_pbmc_data, 
               model_highd = scaled_pbmc_data_model, 
               trimesh_data = tr_from_to_df_pbmc, 
               axis_param = list(limits = 1,
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.48, 
                                 axis_pos_y = -0.48, 
                                 threshold = 0.082))

@@

pbmc_proj_umap_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  axis_text_size = 4,
  is_category = TRUE) + 
  interior_annotation(label = "a2", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

## Second projection
projection <- cbind(
    c(0.0734,0.6138,-0.4671,0.2589,0.1189,0.0778,-0.0819,0.0308,-0.5561),
    c(0.6625,0.0034,0.2412,0.3360,0.2463,0.1070,-0.2903,-0.4705,0.1293))

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 1.25, 
               highd_data = scaled_pbmc_data, 
               model_highd = scaled_pbmc_data_model, 
               trimesh_data = tr_from_to_df_pbmc, 
               axis_param = list(limits = 1.35, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.75, 
                                 axis_pos_y = -0.75, 
                                 threshold = 0.12))

@@

pbmc_proj_umap_model2 <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.5, 0.2), # size, alpha, color
    plot_limits = c(-1, 0.75), 
    axis_text_size = 4,
    is_category = TRUE) +
  interior_annotation(label = "a3", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

pbmc_proj_tsne_model1_best <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  axis_text_size = 4,
  is_category = TRUE) + 
  interior_annotation(label = "b2", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

## Second projection
projection <- cbind(
  c(0.0734,0.6138,-0.4671,0.2589,0.1189,0.0778,-0.0819,0.0308,-0.5561),
  c(0.6625,0.0034,0.2412,0.3360,0.2463,0.1070,-0.2903,-0.4705,0.1293))

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.25, 
                            highd_data = scaled_pbmc_data, 
                            model_highd = scaled_pbmc_data_model, 
                            trimesh_data = tr_from_to_df_pbmc, 
                            axis_param = list(limits = 1.35, 
                                              axis_scaled = 1, 
                                              axis_pos_x = -0.75, 
                                              axis_pos_y = -0.75, 
                                              threshold = 0.12))

@@

pbmc_proj_tsne_model2_best <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1, 0.75), 
  axis_text_size = 4,
  is_category = TRUE) + 
  interior_annotation(label = "b3", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

>>>>

## First projection
projection <- cbind(
  c(0.025588,0.002516,0.002185,0.025284,0.004030,-0.026880,-0.015326,0.014851,0.026260),
  c(0.026495,-0.024817,0.021623,-0.014036,-0.010220,0.016634,-0.006496,-0.022928,0.016045))

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1.23, 
               highd_data = scaled_pbmc_data, 
               model_highd = scaled_pbmc_data_model, 
               trimesh_data = tr_from_to_df_pbmc, 
               axis_param = list(limits = 1,
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.03, 
                                 axis_pos_y = -0.03, 
                                 threshold = 0.0051))

@@

pbmc_proj_umap_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.04, 0.045), 
  axis_text_size = 5,
  is_category = TRUE) + 
  interior_annotation(label = "a2", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

## Second projection
projection <- cbind(
  c(0.025013,0.029055,-0.003143,0.001821,-0.006208,0.019174,0.020630,0.021512,0.020281),
  c(0.004528,0.006465,-0.042452,0.009837,0.010040,-0.023820,0.005236,0.014775,-0.017712))

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 1.25, 
               highd_data = scaled_pbmc_data, 
               model_highd = scaled_pbmc_data_model, 
               trimesh_data = tr_from_to_df_pbmc, 
               axis_param = list(limits = 1.35, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.03, 
                                 axis_pos_y = -0.02, 
                                 threshold = 0.006))

@@

pbmc_proj_umap_model2 <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.5, 0.2), # size, alpha, color
    plot_limits = c(-0.03, 0.03), 
    axis_text_size = 4,
    is_category = TRUE) +
  interior_annotation(label = "a3", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

pbmc_proj_tsne_model1_best <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.04, 0.045), 
  axis_text_size = 4,
  is_category = TRUE) + 
  interior_annotation(label = "b2", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

## Second projection
projection <- cbind(
  c(0.025013,0.029055,-0.003143,0.001821,-0.006208,0.019174,0.020630,0.021512,0.020281),
  c(0.004528,0.006465,-0.042452,0.009837,0.010040,-0.023820,0.005236,0.014775,-0.017712))

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.25, 
                            highd_data = scaled_pbmc_data, 
                            model_highd = scaled_pbmc_data_model, 
                            trimesh_data = tr_from_to_df_pbmc, 
                            axis_param = list(limits = 1.35, 
                                              axis_scaled = 1, 
                                              axis_pos_x = -0.03, 
                                              axis_pos_y = -0.02, 
                                              threshold = 0.006))

@@

pbmc_proj_tsne_model2_best <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.03, 0.03), 
  axis_text_size = 4,
  is_category = TRUE) + 
  interior_annotation(label = "b3", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))
